alluvial diagrams in ggplot2

### 2017-11-18 inst/doc/ggalluvial.rmd

- `x`, the "key" variable indicating the axis to which the row corresponds, which are to be arranged along the horizontal axis;
- `stratum`, the "value" taken by the axis variable indicated by `x`; and
- `alluvium`, the indexing scheme that links the rows of a single alluvium.

>>>>

- `x`, the "key" variable indicating the axis to which the row corresponds, which are to be arranged horizontally;
- `stratum`, the "value" taken by the axis variable indicated by `x`; and
- `alluvium`, the indexing scheme that links the lodes of a single alluvium.
